### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Middle Education Women

Women with one to seven years of education follow a pattern
broadly similar to those with no education as 
Table \ref{tab:median_sex_ratio_med} shows.
The distribution across urban and rural is more even for this education
group than for the no education women.
As a result, the only spells where there are few women to base 
results on are for the fourth spell for urban women and the first 
period of the fourth spell for rural women.

The spacing between births increased over the four decades.
On average, the increase is approximately two months.
The exception is again the first spell, where the time from
marriage to first birth remained the same or fell slightly.

In the period before sex selection became available, 1972--1985,
the differences in spacing between only girls and only boys
increase with spell number.
For both urban and rural women, the difference in duration is just over
a month for the second spell, but it is 1.4 and 2.3 months for urban and
rural women, respectively, for the third spell.
In the three later periods, there is no clear pattern
in the differences across sex compositions.

@@

The decreases in differences are accompanied by increases
in predicted sex ratios, some of which are statistically 
significantly different from the natural sex ratio.
Hence, even though the evidence is not substantial, it does
appear that women with one to seven years of education 
have begun to use sex selection at higher-order spells.
An emerging use of sex selection is also consistent with the falling
fertility for both urban and rural women shown below.

>>>>

Women with one to seven years of education follow a pattern
broadly similar to those with no education as 
Table \ref{tab:median_sex_ratio_med} shows.
The sample size is more evenly distributed across urban and rural 
for this education group than for the no education women.
As a result, the only spells where there are few women to base 
results on are for the fourth spell for urban women and the first 
period of the fourth spell for rural women.

The spacing between births increased over the four decades.
On average, the increase is approximately three to four months.
The exception is again the first spell, where the time from
marriage to first birth remained the same or fell slightly.

In the period before sex selection became available, 1972--1985,
the differences in spacing between only girls and only boys
increase with between the second and third spell.
For both urban and rural women, the difference in duration is just over
a month for the second spell, but it is 1.4 and 2.8 months for urban and
rural women, respectively, for the third spell.
In the three later periods, there is no clear pattern
in the differences across sex compositions.

@@

The decreases in differences are accompanied by increases
in predicted sex ratios, some of which are statistically 
significantly different from the natural sex ratio.
Hence, even though the evidence is not substantial, it does
appear that women with one to seven years of education 
have begun to use sex selection at higher-order spells.
